Cartogram Mapping and Application to Cancer Data.

### 2019-05-06 review_article.Rmd
Structure of review article

---
title: "Review Manuscript"
author: "Stephanie"
date: "02/04/2019"
output: html_document
---

@@

## Spatial Visualisation of Disease Cases

John Snow's use of a map for cholera, cases represented as blocks. Counts within region.

Plotted as points on a map, specific representation of each case.

## Spatial Visualisation of Disease Models

@@

Cartograms stepped toward this goal by highlighting areas of interest. Made some areas bigger on the map space, kept relationship with neighbours.

Importance of the statistic in this area being communicated was more important than keeping geography recognisable.

@@

## Alternative Maps

@@

>>>>

---
title: "Cartogram Mapping and Application to Cancer Data."
output: html_document

toc: true
fig_caption: yes
number_sections: false
fontsize: 11pt
bibliography: reviewbib.bib
biblio-style: vancouver
link-citations: true
---

@@

## Spatial Visualisation of Disease

### Choropleth Map (current go to)

### counts versus predictions

Observed, or predicted.
Challenges for either.

@@

## Cartograms

General introduction:
Cartograms stepped toward this goal by highlighting areas of interest. Made some areas bigger on the map space, kept relationship with neighbours.
USA regular cartogram (UK too)

### Contiguous
Importance of the statistic in this area being communicated was more important than keeping geography recognisable.

@@

### Non-Contiguous

Dorling (Sized according to statistic)

## Temporal displays

## Alternatives

Plotting centroids on top of geographies. (Size is kept constant)
Hexmaps

@@

## Comparison of 
(only worth including if it is possible for us to implement)
Tabular form comparing and contrasting
- Relationship to geography

- Show using cancer examples

## Animation

lends to temporal pattern exploration

## Software
Commonly available tools to implement.
